A tale of two cities: A data synthesis approach for semantic decompositions of Twitter user locations

### 2016-08-21 semantic_decomposition_of_twitter_user_locations/paper.tex
mac

\begin{document}
\title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\author[1]{Junjun Yin\thanks{yinjunjun@gmail.com}}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}
Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a scalable data integration 
We analyzed the

\section{Introduction}

@@

>>>>

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A data synthesis approach for semantic decompositions of Twitter user locations}
\author[1~\thanks{yinjunjun@gmail.com}]{Junjun Yin}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}

Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a scalable data integration 
We analyzed the

\section{Introduction}
Today's pervasive Location Based Social Media (LBSM) are attacting much attention from many researh displines. For example,

@@

\subsection{A scalable data synthesis framework}
